Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-03-21 article.rnw
Change the inspecific subjecct "this" to "this result".

% DBS: Avoid imprecise "this" or "that" as subjects. Always say "This result" or something similar. Also, avoid starting a new paragraph that so strongly forms a continuation of the previous one.
This stands in contrast to the popular wisdom in ecology that species should form some sort of clear groups, be they the functional groups so often used \parencite{blondel2003guilds}, or taxonomic groups per a relationship between phylogeny and ecological niche \parencite{godoy2014phylogenetic}.
It also contrasts with previous studies that have succeeded in finding clear groups, such as \textcite{allesina2009food}, who used AIC to find the best grouping of species, but in a binary food web rather than a quantitative competitive context.
Perhaps species simply do not group to the same extent in a competitive context.
The results suggest that this is unlikely, as grouping was still likely to increase parsimony.
Further, there is no reason to suspect that species would not have clear similarities or dissimilarities in their ecological niches, and therefore their competitive effects and responses.
Perhaps the lack of clarity in the groupings is instead a product of the study system chosen.

>>>>

% DBS: Avoid imprecise "this" or "that" as subjects. Always say "This result" or something similar. Also, avoid starting a new paragraph that so strongly forms a continuation of the previous one.
This result stands in contrast to the popular wisdom in ecology that species should form some sort of clear groups, be they the functional groups so often used \parencite{blondel2003guilds}, or taxonomic groups per a relationship between phylogeny and ecological niche \parencite{godoy2014phylogenetic}.
It also contrasts with previous studies that have succeeded in finding clear groups, such as \textcite{allesina2009food}, who used AIC to find the best grouping of species, but in a binary food web rather than a quantitative competitive context.
Perhaps species simply do not group to the same extent in a competitive context.
The results suggest that this is unlikely, as grouping was still likely to increase parsimony.
Further, there is no reason to suspect that species would not have clear similarities or dissimilarities in their ecological niches, and therefore their competitive effects and responses.
Perhaps the lack of clarity in the groupings is instead a product of the study system chosen.
